---
title: "`r input$report.title`"
subtitle: "`r input$report.subtitle`"
authors: "`r input$report.authors`"
date: "`r Sys.Date()`"
---

```{r setup, echo=FALSE}
library(knitr)
library(BBmisc)
opts_chunk$set(size = "footnotesize", echo = FALSE)
options(digits = 3L)
reqReactive = function(reac) {
  tryCatch(reac, error = function(err) NULL)
}
````

```{r testchunk,echo=FALSE}
# :D
```


```{r data.prep}
df = data$data
sum.vis = reqReactive(summary.vis.collection)
eval.sum.vis = all(params$include$data, !is.null(sum.vis$var.plots))
params$titles$data = ifelse(params$include$data, params$titles$data, "")
```

#`r params$titles$data`

`r params$passage$data`

```{r data,include=params$include$data}
kable(summarizeColumns(df))
```

```{r data.vis.prep,eval=eval.sum.vis}
for (i in seq_along(sum.vis$var.names)) {
  q = sum.vis$var.plots[[sum.vis$var.names[i]]]
  q = q + ggtitle(sum.vis$var.names[i])
  print(q)
}
```

\newpage


```{r task.prep}
task = reqReactive(task.out())
params$include$task = all(params$include$task, !is.null(task))
params$titles$task = ifelse(params$include$task, params$titles$task, "")
out.task = ""
```

#`r params$titles$task`

`r params$passage$task`

```{r task,eval=params$include$task}
#FIXME: make task dep
tar.name = knit_expand(text="**Target name:** {{getTaskTargetNames(task)}} \n")
tar.levs = paste("**Target levels:** ", collapse(getTaskClassLevels(task), sep = ", "),
  "\n")
tar.levs = knit_expand(text=tar.levs)
n.obs = knit_expand(text="**Number of observations:** {{getTaskSize(task)}} \n")
n.feats = knit_expand(text="**Number of features:** {{getTaskNFeats(task)}} \n")
out.task = c(tar.name, tar.levs, n.obs, n.feats)
```

`r paste(knit(text = out.task), collapse = '\n')`

\newpage


```{r learners.prep,include=params$include$learners}
learners = reqReactive(learners())
learners.par.sets = reqReactive(learners.par.sets())
eval.learners = all(!is.null(learners), params$include$learners)
params$include$learners = all(params$include$learners, eval.learners)
params$titles$learners = ifelse(params$include$learners,
  params$titles$learners, "")
out.lrns = ""
```

#`r params$titles$learners`

`r params$passage$learners`

```{r learners,eval=eval.learners,results="asis"}
# FIXME: Put in datatables for HTML files when we implement interactive code chunks
out.lrns = NULL
lrn.names = names(learners)
for (i in seq_along(learners.par.sets)) {
  par.set = ParamHelpers:::getParSetPrintData(learners.par.sets[[i]])
  lrn.name = knit_expand(text="### {{lrn.names[i]}} \n")
  if (input$report.format == "PDF") {
    tab = knit_expand(text="{{kable(par.set)}} \n")
    # cat("\n")
  } else {
    # DT::datatable(par.set)
    tab = kable(par.set)
    # cat("\n")
  }
  out.lrns = c(out.lrns, lrn.name, tab)
}
```

`r paste(knit(text = out.lrns), collapse = '\n')`

\newpage


```{r modelling.prep}
model = reqReactive(model())
measures.perf = reqReactive(measures.perf())
eval.model = all(!is.null(model), !is.null(measures.perf))
params$include$modelling = all(params$include$modelling, eval.model)
pred.plots = reqReactive(prediction.plot.collection)
# pred.plots = pred.plots$pred.plots
eval.pred.plots = all(params$include$modelling, !is.null(pred.plots))
params$titles$modelling = ifelse(params$include$modelling,
  params$titles$modelling, "")
```

#`r params$titles$modelling`

`r params$passage$modelling`


```{r modelling,eval=eval.model}
# print(model)
# preds = predict(model, task)
# preds$data
# performance(preds, measures.perf)
```

```{r pred.plots,eval=TRUE}
for (i in seq_along(pred.plots$plot.titles)) {
  q = pred.plots$pred.plots[[pred.plots$plot.titles[i]]]
  # q = q + ggtitle(sum.vis$var.names[i])
  print(q)
}
# lapply(pred.plots, renderPlot)
```

\newpage


```{r tuning.prep}
tune.res = reqReactive(tuning())
# measures.perf = reqReactive(measures.perf())
eval.tuning = all(!is.null(tune.res), !is.null(params$include$tuning))
params$include$tuning = all(params$include$tuning, eval.tuning)
params$titles$tuning = ifelse(params$include$tuning,
  params$titles$tuning, "")
```

#`r params$titles$tuning`

`r params$passage$tuning`

```{r tuning,include=params$include$tuning}
names(tune.res)
# tune.res$opt.path
# names(tune.res$opt.path)
# tune.res$learner
tune.res$x
tune.res$y
```

\newpage


```{r benchmark.prep}
bmr = reqReactive(bmr())
# measures.perf = reqReactive(measures.perf())
eval.benchmark = all(!is.null(bmr), !is.null(params$include$benchmark))
params$include$benchmark = all(params$include$benchmark, eval.benchmark)
bmr.plots = reqReactive(bmr.plots.collection)
eval.bmr.plots = all(params$include$benchmark, !is.null(bmr.plots))
params$titles$benchmark = ifelse(params$include$benchmark,
  params$titles$benchmark, "")
```

#`r params$titles$benchmark`

`r params$passage$benchmark`

```{r benchmark,include=params$include$benchmark}
#coming soon
```

```{r bmr.plots,eval=eval.bmr.plots}
for (i in seq_along(bmr.plots$plot.titles)) {
  q = bmr.plots$bmr.plots[[bmr.plots$plot.titles[i]]]
  print(q)
}
```


